Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-25 docs/manuscript/manuscript.tex
Edit of introduction.

Globally, access to improved drinking water sources and sanitation is increasing. From 1990 to 2012, the utilization of
improved drinking water sources has increased globally from 76 percent to 89 percent, and utilization of improved
sanitation has increased from 45 percent to 64 percent \citep{fuller2016tracking}. According to the Millennium Development Goals (MDGs),
they consider improved drinking water sources as the following: public tap, borehole, protected spring, rainwater
collection, bottled water source, and piped water \citep{bartram_global_2014}. However, these variables do not truly
explain if the households have speedy access to retrieve the water. Additionally, \citet{graham_analysis_2016} investigated that many people in sub-Saharan Africa (SSA) leave their homes to retrieve water, potentially placing them at risk for varieties of negative health outcomes. There are estimation of 3.36 million children and 13.54 million adult females were responsible for collection in households with fetching times greater than 30 minutes \citep{graham_analysis_2016}.

>>>>

Globally, access to improved drinking water sources and sanitation is increasing. From 1990 to 2012, the utilization of
improved drinking water sources has increased globally from 76 percent to 89 percent, and utilization of improved
sanitation has increased from 45 percent to 64 percent \citep{fuller2016tracking}. According to the Millennium Development Goals (MDGs),
they consider improved drinking water sources like the following: public tap, borehole, protected spring, rainwater
collection, bottled water source, and piped water \citep{bartram_global_2014}. However, these variables do not truly
explain if the households have speedy access to retrieve the water. Additionally, \citet{graham_analysis_2016} investigated that many people in sub-Saharan Africa (SSA) leave their homes to retrieve water, potentially placing them at risk for a variety of negative health outcomes. There are an estimation of 3.36 million children and 13.54 million adult females were responsible for collection in households with fetching times greater than 30 minutes \citep{graham_analysis_2016}. Therefore, there needs to be a way to alleviate people's burdens to retrieve water and potentially investigate water accessibility improving variables.
